Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-22 03-architecture.tex
Some updates to table 1.
Get rid of colorbox.

\begin{tcolorbox}[title=ANTHONY AND SERGE]
You might notice that there is no mention of "Napali" or "Laha" in this paper. I could not think of a good way to add them in that would not additionally complicate any already terminologically complicated topic. To me, they feel like "overlays" onto the four component architecture described here and thus not strictly necessary to understand the system, but let me know if you disagree.
\end{tcolorbox}

@@

To address these requirements, the OPQ information architecture is organized as a five layer pyramid as summarized in Table \ref{fig:information-architecture}. This table illustrates an important conceptual feature of the OPQ information architecture called ``TTL'', or Time To Live. The OPQ information architecture implements an active, ``use it or lose it'' approach to information management, in which a data item must either be associated with a higher level of the system within its Time To Live, or else it will be automatically deleted. So, for example, the high fidelity waveform data on an OPQ Box have a TTL of one hour: if that data is not requested from a box by a higher layer in the information architecture within an hour of it being generated, it will be lost. Similarly, data points in the Measurement layer will be deleted after one day if they are not associated with an Event. Details of this hierarchy are further explained in Section~\ref{sec:opq-mauka}.

@@

>>>>

@@

To address these requirements, the OPQ information architecture is organized as a five layer pyramid as summarized in Table \ref{fig:information-architecture}. This table illustrates an important conceptual feature of the OPQ information architecture called ``TTL'', or Time To Live. The OPQ information architecture implements an active, ``use it or lose it'' approach to information management, in which a data item must either be associated with a higher level of the system within its Time To Live, or else it will be automatically deleted. So, for example, the high fidelity waveform data on an OPQ Box have a TTL of one hour: if that data is not requested from a box by a higher layer in the information architecture within an hour of it being generated, it will be lost. Similarly, data points in the Measurement layer will be deleted after one day if they are not associated with an Event.

@@

Further details of this hierarchy are provided in Section~\ref{sec:opq-mauka}.
